Kate chronic samples

### 2019-11-19 scripts/z01_kate_sample_sort.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
source('~/MSK/work/microbiome_db/SQL/scripts/get_data_from_query_OTU.R')
```

```{r}
chronic <- get_data_from_query_OTU(0,'frozen_set_cgvhd_ag')
```

@@

period_list <- chronic %>% 
  select(patient_id, sampleid, case_status, day_relative_to_hct) %>% 
  mutate(period = case_when(
    day_relative_to_hct >= -30 & day_relative_to_hct <= -6 ~ 'PreHCT',
    day_relative_to_hct >= 7 & day_relative_to_hct <= 21 ~ 'PeriHCT',
    day_relative_to_hct >= 70 & day_relative_to_hct <= 130 ~ 'PeriD100'
  )) %>% 
  # keep the records that are in the above periods
  filter(!is.na(period)) %>% 
  split(.$period)

@@

# target samples
target <- period_diff %>% 
  group_by(patient_id, period) %>% 
  arrange(tdiff, .by_group = T) %>% 
  slice(1)  %>% 
  arrange(period, tdiff, sampleid)

# how many unique patients
period_diff %>% 
   group_by(patient_id) %>% 
   summarise(cnt = n())
```

```{r}
# how many we actually have shotgun
catalog <- read_csv('/Volumes/vandenBrinkLab/Angel_Dai/Full_human_shotgun_catalog/full_human_shotgun_catalog_updated.csv')

target_have <- target %>% 
  inner_join(catalog, by = 'sampleid') %>% 
  # only looking at the PeriD100 time
  filter(period == 'PeriD100')

current <- read_csv('~/projects/MSS_pipeline-/output/current_240_sample_preprocessing_stats.csv')

# how many we actually have 
length(intersect(current$sampleid, target_have$sampleid))

@@

# how many need to be uploaded (35)
target_have %>% 
  filter(!sampleid %in% current$sampleid) %>% 
  select(directory) %>% 
  mutate(cmd = str_glue('rsync --progress --partial -avz {directory} daia1@lilac.mskcc.org:~/my_workdir/samples/kate')) %>% 
  ungroup() %>%
  select(cmd) %>%  
  write_csv('../data/upload_kate_70.sh', col_names = F)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggvenn)
source('~/MSK/work/microbiome_db/SQL/scripts/get_data_from_query_OTU.R')
```

**So the key is that first you filter on the samples that have shotgun data!!!! **
**And then select the ones that are the closest !!! so that you don't waste any shotgun data!!!!!**

```{r}
chronic <- get_data_from_query_OTU(0,'frozen_set_cgvhd_ag')

# how many we actually have shotgun
catalog <- read_csv('/Volumes/vandenBrinkLab/Angel_Dai/Full_human_shotgun_catalog/full_human_shotgun_catalog_updated.csv')

chronic_shot <- chronic %>% 
  inner_join(catalog, by = 'sampleid')
```

@@

period_list <- chronic_shot %>% 
  select(patient_id, sampleid, case_status, day_relative_to_hct, directory) %>% 
  mutate(period = case_when(
    day_relative_to_hct >= -30 & day_relative_to_hct <= -6 ~ 'PreHCT',
    day_relative_to_hct >= 7 & day_relative_to_hct <= 21 ~ 'PeriHCT',
    day_relative_to_hct >= 70 & day_relative_to_hct <= 130 ~ 'PeriD100'
  )) %>% 
  # keep the records that are in the above periods
  filter(!is.na(period)) %>% 
  split(.$period)

@@

# target samples 
target <- period_diff %>% 
  filter(period == 'PeriD100') %>% 
  group_by(patient_id) %>% 
  arrange(tdiff, .by_group = T) %>% 
  slice(1)  %>% 
  arrange(patient_id, tdiff, sampleid) %>% 
  distinct(sampleid, .keep_all = T)

target %>% 
  write_csv('../data/kate/final_p100_sample.csv')

```

```{r}
current <- read_csv('~/projects/MSS_pipeline-/output/current_240_sample_preprocessing_stats.csv')

# how many we actually have 
length(intersect(target$sampleid, current$sampleid))

@@

# how many need to be uploaded (35)
target %>% 
  filter(!sampleid %in% current$sampleid) %>% 
  select(directory) %>% 
  mutate(cmd = str_glue('rsync --progress --partial -avz {directory} daia1@lilac.mskcc.org:~/my_workdir/samples/kate')) %>% 
  ungroup() %>%
  select(cmd) %>%  
  write_csv('../data/upload_kate_43.sh', col_names = F)
```
